\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-10-27 paper.tex
Updates from Overleaf

ARG-unary nodes occur when an ARG node has one child and one or
more parents.
Nodes with one child and one parent (``pass-through'' nodes)
occur where we wish the record the passage of ancestral material
through a known node. For example, in simulations
it is sometimes useful to record the passage of
ancestral material through known pedigree individuals
regardless of whether common ancestry occurs.
ARG-unary nodes are also occur in inferences
from longitudinal datasets where genetic
data is sampled at many timepoints and recombination
is rare (e.g.~SARS-CoV-2; see Discussion).
Nodes with one child and two parents arise when
we model a recombination event using a single node
in the classical manner
(e.g.\ Fig.~\ref{fig-ancestry-resolution}).

>>>>

An ARG node with one child and one or
more parents is ARG-unary.
If it has one child and only one parent, it represents a ``pass-through'' node:
these occur where we wish the record the passage of ancestral material
through a known node. For example, in simulations
it is sometimes useful to record the passage of
ancestral material through known pedigree individuals
regardless of whether common ancestry occurs.
Nodes with one child and two parents arise when
we model a recombination event using a single node
in the classical manner
(e.g.\ Fig.~\ref{fig-ancestry-resolution}).
It is also possible for sample nodes to be ARG-unary, for example
in inferences from longitudinal datasets where genetic
data is sampled at many timepoints and recombination
is rare (e.g.~SARS-CoV-2; see Discussion).
